A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-09 survey.tex
Reviewed Sections I and II.

Complex dynamic environments, where it is not possible to have perfect nor complete information about the current state or about the dynamics of the environment, pose significant challenges for artificial intelligence. Road  traffic, finance, or
weather  forecasts are  examples of such large, complex, real-life dynamic
environments. RTS games can be seen as a simplification of a real-life
environment, with simpler dynamics in a  finite and smaller
world, although still complex enough  to bring very difficult and interesting
problems  to  the scientific  community like  decision making  under
uncertainty  or  real-time adversarial planning. Finding efficient  techniques for
tackling  these problems  on  RTS  games can  thus  benefit broader  AI
domains, but  also have concrete  and direct applications in  the ever growing
industry of  video games.%, generating worldwide two  and a  half times more revenue than the Film industry in 2011.
% This statement is not fair, the reference I found it only compare all the game industry revenue (including hardware sales) vs theatrical film industry revenue (i.e. not DVD sales, ...)

This paper, aiming to provide a one-stop guide on what is the state of
the art in RTS AI, and with a particular emphasis on the work done in StarCraft. 
It is organized as follows: Section~\ref{sec:rts}
introduces real-time strategy games, in particular the game StarCraft,
and  the main  AI challenges  in RTS  games.  Section~\ref{sec:review}
reviews  the existing  work on tackling these challenges in RTS games.
Section~\ref{sec:bot} analyzes several current state of the art RTS game playing agents (called {\em bots}), selected form the participants to annual
StarCraft    AI    competitions.
Section~\ref{sec:competition}  presents results of the recent annual competitions
held at the AIIDE  and CIG conferences and a StarCraft bot game ladder\footnote{An extended tournament, which can potentially go on indefinitely.}.  Section~\ref{sec:questions}
compiles open questions in RTS game AI. Finally, the paper concludes on discussions and perspectives.

@@

\begin{itemize}
\item They are {\em simultaneous move} games, where more than one player can issue actions at the same time. Additionally, these actions are {\em durative}, i.e. actions are not instantaneous, but take some amount of time time to complete.
\item RTS games are ``real-time'', which actually means is that each player has a very small amount of time to decide the next move. Compared to Chess, where players have several minutes to decide the next action, in StarCraft, the game executes at 24 iterations per second, which means that players only have 55ms to decide a move, before the game state changes.
\item Most RTS games are partially observable: players can only see the part of the map that has been explored.
\item Most RTS games are non-deterministic. Some actions have a chance of success.
\item And finally, the complexity of these games, both in terms of state space size and in terms of number of actions available at each decision cycle is very large. For example, the state space of Chess is typically estimated to be around $10^{50}$, heads up no-limit texas holdem poker around $10^{80}$, and Go around $10^{170}$. In comparison, the state space of StarCraft in a typical map is estimated to be many orders of magnitude larger than any of those, as discussed in the next section.
\end{itemize}

@@

\begin{itemize}
	\item Terrans, provide units that are versatile and flexible giving a balanced option between Protoss and Zergs.
	\item Protoss units have lengthy and expensive manufacturing process, but they are strong and resistant. These conditions makes players follow a strategy of quality over quantity.
	\item Zergs, the insectoid race, units are cheap and weak. They can be produced fast, encouraging players to overwhelm their opponents with sheer numbers.
\end{itemize}

Figure~\ref{fig:StarCraft} shows a screenshot of StarCraft showing a player playing Terrans. In order to win a StarCraft game, players must first gather resources (minerals and Vespene gas). As resources become available, players need to allocate them for creating more buildings (which reinforce the economy, and allow players to create units or unlock stronger units), research new technologies (in order to use new unit abilities or improve the units) and train attack units. Units must be distributed to accomplish different tasks such as reconnaissance, defense and attack. While performing all of those tasks, players also need to strategically understand the geometry of the map at hand, in order to decide where to place new buildings (concentrate in a single area, or expand to different areas) or where to set defensive outposts. Finally, when offensive units of two players meet, each player must quickly maneuver each of the units in order to fight a battle, which requires quick and reactive control of each of the units in order to successfully fight the battle.

@@

A typical StarCraft map is defined as a rectangular grid, where the $width \times height$ of the map is measured in the number of $32 \times 32$ square of pixels, a.k.a build tiles. Although the
resolution  at which  units  move  is in squares of $8 \times 8$ pixels, a.k.a walk tiles. The standard dimensions are 64, 96, 128, 192 and 256. Each player  can
control up  to 200 units (not including  buildings).  Moreover, each
different race  contains between 30  to 35 different types  of units
and  buildings,  each  one  with  a significant  number  of  special
abilities. All these factors  together make StarCraft a significant
challenge,   in   which   humans    are   still   much   better   than
computers. For instance, in the game ladder iCCup\footnote{http://www.iccup.com/StarCraft/} where users are ranked by their current point totals: $E$ being the lowest possible rank, and $A^+$ and $Olympic$ being the second highest and highest ranks, respectively. Best StarCraft AI bots are ranked between $D$ and $D^−$, where average  amateur players are  ranked between $C^+$ and  $B$. For comparison, StarCraft professional  players are usually ranked between
$A^-$ and $A^+$.

From a theoretical point of view, the state space of a StarCraft for a given map is enormous. For example, consider a 128x128 map. At any given moment there might be between 50 to 400 units in the map, each of which might have a complex internal state (remaining energy and hit-points, action being executed, etc.). Which, quickly lead to an immense number of possible states (way beyond the size of smaller games, such as Chess or Go). For example, just considering the location of each unit, we might have 128x128 possible positions per unit, and 400 units, giving us an initial number of $16384^{400} \approx 10^{1685}$. If we add the other factors playing a role in the game, we obtain even larger numbers.

Another way  to measure the complexity  of the game, is  by looking at
the branching factor, $b$ and the depth of the game, $d$, as proposed in~\cite{Gaby}. In Chess, $b \approx 35$ and $d \approx 80$. In more complex games, like Go, $b \approx 30 - 300$, and $d \approx 150 - 200$. In StarCraft, humans can issue only one action at a time (this is because of the GUI used by the game, computer players can issue several actions, to different units, at any given time), thus, assuming a player controls between 50 to 200 units, and that each unit can execute between 4 to 20 actions (moving in each of the 4 cardinal directions, attacking units in range, use special abilities, etc.), we obtain a branching factor $b \approx 200 - 4000$. Good players can execute about 300 actions per minute, and the typical length of a game is about 25 minutes. Thus, $d \approx 7500$.

@@

\subsubsection{Planning}
As mentioned above, the size of the state space in RTS games is vastly larger than that of traditional board-games such as Chess or Go. Additionally, the number of actions that can be executed at a given instant of time is also much larger. Thus, standard adversarial planning approaches, such as game tree search are not directly applicable. As we elaborate later, planning in RTS games can be seen as having multiple levels of abstraction: at a higher level, players need long-term planning capabilities, in order to develop a strong economy in the game; at a low level, individual units need to be moved in coordination to fight battles taking into account the terrain and the opponent. Techniques that can address this large planning problems by either sampling, or hierarchical decomposition do not yet exist.

\subsubsection{Learning}
Given the difficulties in playing RTS games by directly using adversarial planning techniques, many research groups have turned attention to learning techniques. We can distinguish three types of learning problems in RTS games:
\begin{itemize}
\item {\em Prior learning}: How can we exploit available data, such as existing replays, or information about specific maps for learning appropriate strategies before hand? A significant amount of work has gone in this direction.%, such as \cite{WeberCIG09,SynnaeveCIG11,SynnaeveAIIDE11,OntanonMSR10}.
\item {\em In-game learning}: How can bots deploy online learning techniques that allow them to improve their game play while playing a game? These techniques might include reinforcement learning techniques, but also opponent modeling. The main problem again is the fact that the state space is too large and the fact that RTS games are partially observable.
\item {\em Inter-game learning}: What can be learned from one game that can be used to increase the chances of victory in the next game? Some work has used simple game-theoretical solutions to select amongst a pool of predefined strategies, but the general problem remains unanswered.
\end{itemize}

@@

\subsubsection{Spatial and Temporal Reasoning}
% TODO just a paragraph on exposing why there are temporal and spatial
% reasoning in RTS AI.
Spatial  reasoning   is  related  to   each  aspect  of   the  terrain
exploitation.  Spatial reasoning is involved in tasks such as building placing, or base expansion. In the former, the player needs to
carefully  consider buildings  position  into its  own  bases to  both
protect them  by creating  a wall against  invasions and to  avoid bad
configurations  where large  units could  be stuck. In base expansion, the player has to
choose good available emplacements to  build a new base, regarding its
own  position  and opponent's  bases.  Finally,  spatial reasoning  is
key to tactical reasoning: players need to decide where to place units
for battle,  favoring, for  instance, engagements when  the opponent's
units are into a bottleneck.

@@

Analogously, temporal reasoning is key in tactical or strategic reasoning. For example, timing attacks and retreats to gain advantage. At a higher strategic level, players need to reason about when to perform long-impact economic actions such as upgrades, building construction, strategy switching, etc. all taking into account that the effects of these actions are not immediate, but longer term.

\subsubsection{Domain Knowledge Exploitation}
In traditional board-games such as Chess, researchers have exploited the large amounts of existing domain knowledge to create good evaluation functions to be used by alpha-beta search algorithms, extensive opening books, or end-game tables. In the case of RTS games, it is still unclear the ways in which the significantly large amount of domain knowledge (in the forms or strategy guides, replays, etc.) can be exploited by bots. Most work in this area has focused on two main directions: on the one hand, researchers are finding ways in which to hard-code existing strategies into bots, so that bots only need to decide which strategies to deploy, instead of having to solve the complete problem of deciding which actions to execute by each individual unit at each time step. One the other hand, large datasets of replays have been created \cite{WeberCig09, synnaeve2012dataset}, from where strategies, trends or plans have been tried to learn. However, StarCraft games are quite complex, and how to automatically learn from such datasets is still an open problem.

\subsubsection{Task Decomposition}
For all the previous reasons, most existing approaches to play games like StarCraft work by decomposing the problem of playing a RTS game into a collection of smaller problems, to be solved independently. Specifically, a common subdivision is:
\begin{itemize}
\item {\em Strategy}: corresponds to the high-level decision making process.  This is
  the  highest level of  abstraction for  the game  comprehension. RTS
  games   are   all   about   finding   an   efficient   strategy   or
  counter-strategy  against a  given opponent.  It concerns  the whole
  set of  units and buildings  one owns. %If  we may allow  ourselves a  military analogy, strategy is orders given by generals at the HQ. 
\item  {\em Tactics}: are  the implementation  of the  current  strategy. It
  implies  army and  building positioning,  movements, timing,  and so
  on.  Tactics concerns a  group of  units. %They  are orders  given by officers on the battlefield.
\item  {\em Reactive  control}: is  the  implementation  of  tactics.  This
  consists   in  moving,   targeting,  firing,   fleeing,  hit-and-run
  techniques (a.k.a. ``kiting'')  during battle. Reactive control focuses
  on a specific unit. %It is soldiers applying officers' orders. 
%\end{itemize}
%
%\noindent
%Both     strategy      and     tactics     are      usually     called
%\textit{macro-management},  whereas reactive  control  is also  called
%\textit{micro-management}. In addition of the three tasks shown above,
%one could also consider these two tasks that an AI has to deal with:
%\begin{itemize}
\item {\em Terrain analysis}: consists  in the analysis of regions composing
  the  map:  choke-points,  minerals  and  gas emplacements,  low  and  high
  walkable grounds, islands, etc.
\item {\em Intelligence gathering}:  corresponds to information collected about
  the  opponent. Because of  the fog-of-war,  players must
  regularly send scouts to localize and spy enemy bases.%, and must see or  infer what buildings and technology the enemy has developed in order  to adapt its strategy.
\end{itemize}

We want to mention also the task decomposition that the gamer community do. Given the fact that players cannot perform multiple actions at the same time, they divide their tasks in two groups:
\begin{itemize}
  \item {\em Macro}: is the ability to control your units individually. A good \emph{macro} player usually keeps their units alive during more time.
  \item {\em Micro}: is the ability to produce units and to expand at the appropriate times to keep your production of units flowing. A good \emph{micro} player usually has the larger army.
\end{itemize}

The reader can find a  good presentation of task decomposition for AIs
playing RTS in~\cite{weber2011acs}. Although the previous task decomposition is common, a significant challenge is on designing architectures so that the individual AI techniques that address each of those tasks can communicate and effectively work together, resolving conflicts, prioritizing resources between them, etc.

>>>>

Complex dynamic environments, where it is not possible to have perfect nor complete information about the current state or about the dynamics of the environment, pose significant challenges for artificial intelligence. Road  traffic, finance, or
weather  forecasts are  examples of such large, complex, real-life dynamic
environments. RTS games can be seen as a simplification of one such real-life
environment, with simpler dynamics in a  finite and smaller
world, although still complex enough  to study some of the key interesting
problems like decision making  under
uncertainty  or  real-time adversarial planning. Finding efficient  techniques for
tackling  these problems  on  RTS  games can  thus  benefit other AI disciplines and application
domains, ans also have concrete  and direct applications in  the ever growing
industry of  video games.%, generating worldwide two  and a  half times more revenue than the Film industry in 2011.
% This statement is not fair, the reference I found it only compare all the game industry revenue (including hardware sales) vs theatrical film industry revenue (i.e. not DVD sales, ...)

This paper aims to provide a one-stop guide on what is the state of
the art in RTS AI, with a particular emphasis on the work done in StarCraft. 
It is organized as follows: Section~\ref{sec:rts}
introduces RTS games, in particular the game StarCraft,
and  their main  AI challenges.  Section~\ref{sec:review}
reviews  the existing  work on tackling these challenges in RTS games.
Section~\ref{sec:bot} analyzes several current state of the art RTS game playing agents (called {\em bots}), selected form the participants to annual
StarCraft    AI    competitions.
Section~\ref{sec:competition}  presents results of the recent annual competitions
held at the AIIDE  and CIG conferences and a StarCraft bot game ladder\footnote{An extended tournament, which can potentially go on indefinitely.}.  Section~\ref{sec:questions}
compiles open questions in RTS game AI. Finally, the paper concludes on discussions and perspectives.

@@

\begin{itemize}
\item They are {\em simultaneous move} games, where more than one player can issue actions at the same time. Additionally, these actions are {\em durative}, i.e. actions are not instantaneous, but take some amount of time time to complete.
\item RTS games are ``real-time'', which actually means is that each player has a very small amount of time to decide the next move. Compared to Chess, where players have several minutes to decide the next action, in StarCraft, the game executes at 24 iterations per second, which means that players only have 55ms to decide a move, before the game state changes.
\item Most RTS games are partially observable: players can only see the part of the map that has been explored. This is referred to as the {\em fog-of-war}.
\item Most RTS games are non-deterministic. Some actions have a chance of success.
\item And finally, the complexity of these games, both in terms of state space size and in terms of number of actions available at each decision cycle is very large. For example, the state space of Chess is typically estimated to be around $10^{50}$, heads up no-limit texas holdem poker around $10^{80}$, and Go around $10^{170}$. In comparison, the state space of StarCraft in a typical map is estimated to be many orders of magnitude larger than any of those, as discussed in the next section.
\end{itemize}

@@

\begin{itemize}
	\item Terrans, provide units that are versatile and flexible giving a balanced option between Protoss and Zergs.
	\item Protoss units have lengthy and expensive manufacturing process, but they are strong and resistant. These conditions make players follow a strategy of quality over quantity.
	\item Zergs, the insectoid race, units are cheap and weak. They can be produced fast, encouraging players to overwhelm their opponents with sheer numbers.
\end{itemize}

Figure~\ref{fig:StarCraft} shows a screenshot of StarCraft showing a player playing Terrans. In order to win a StarCraft game, players must first gather resources (minerals and Vespene gas). As resources become available, players need to allocate them for creating more buildings (which reinforce the economy, and allow players to create units or unlock stronger units), research new technologies (in order to use new unit abilities or improve the units) and train attack units. Units must be distributed to accomplish different tasks such as reconnaissance, defense and attack. While performing all of those tasks, players also need to strategically understand the geometry of the map at hand, in order to decide where to place new buildings (concentrate in a single area, or expand to different areas) or where to set defensive outposts. Finally, when offensive units of two players meet, each player must quickly maneuver each of the units in order to fight a battle, which requires quick and reactive control of each of the units.

@@

A typical StarCraft map is defined as a rectangular grid, where the $width \times height$ of the map is measured in the number of $32 \times 32$ square of pixels, a.k.a build tiles. Although the
resolution  at which  units  move  is in squares of $8 \times 8$ pixels, a.k.a walk tiles. The typical dimensions for maps range from $64 \times 64$ to $256 \times 256$ build tiles. Each player  can
control up  to 200 units (not including  buildings).  Moreover, each
different race  contains between 30  to 35 different types  of units
and  buildings,  each  one  with  a significant  number  of  special
abilities. All these factors  together make StarCraft a significant
challenge,   in   which   humans    are   still   much   better   than
computers. For instance, in the game ladder iCCup\footnote{http://www.iccup.com/StarCraft/} where users are ranked by their current point totals ($E$ being the lowest possible rank, and $A^+$ and $Olympic$ being the second highest and highest ranks, respectively), the best StarCraft AI bots are ranked between $D$ and $D^+$, where average  amateur players are  ranked between $C^+$ and  $B$. For comparison, StarCraft professional  players are usually ranked between
$A^-$ and $A^+$.

From a theoretical point of view, the state space of a StarCraft for a given map is enormous. For example, consider a 128x128 map. At any given moment there might be between 50 to 400 units in the map, each of which might have a complex internal state (remaining energy and hit-points, action being executed, etc.). This quickly leads to an immense number of possible states (way beyond the size of smaller games, such as Chess or Go). For example, just considering the location of each unit (with 128x128 possible positions per unit), and 400 units, gives us an initial number of $16384^{400} \approx 10^{1685}$. If we add the other factors playing a role in the game, we obtain even larger numbers.

Another way  to measure the complexity  of the game is  by looking at
the branching factor, $b$, and the depth of the game, $d$, as proposed in~\cite{Gaby}. In Chess, $b \approx 35$ and $d \approx 80$. In more complex games, like Go, $b \approx 30 - 300$, and $d \approx 150 - 200$. In StarCraft, humans can issue only one action at a time (this is because of the GUI used by the game, computer players can issue several actions, to different units, at any given time), thus, assuming a player controls between 50 to 200 units, and that each unit can execute between 4 to 20 actions (moving in each of the 4 cardinal directions, attacking units in range, use special abilities, etc.), we estimate the branching factor for human players to be around $b \approx 200 - 4000$. Good players can execute about 300 actions per minute, and the typical length of a game is about 25 minutes. Thus, $d \approx 7500$.

@@

\subsubsection{Planning}
As mentioned above, the size of the state space in RTS games is much larger than that of traditional board-games such as Chess or Go. Additionally, the number of actions that can be executed at a given instant of time is also much larger. Thus, standard adversarial planning approaches, such as game tree search are not directly applicable. As we elaborate later, planning in RTS games can be seen as having multiple levels of abstraction: at a higher level, players need long-term planning capabilities, in order to develop a strong economy in the game; at a low level, individual units need to be moved in coordination to fight battles taking into account the terrain and the opponent. Techniques that can address these large planning problems by either sampling, or hierarchical decomposition do not yet exist.

\subsubsection{Learning}
Given the difficulties in playing RTS games by directly using adversarial planning techniques, many research groups have turned attention to learning techniques. We can distinguish three types of learning problems in RTS games:
\begin{itemize}
\item {\em Prior learning}: How can we exploit available data, such as existing replays, or information about specific maps for learning appropriate strategies before hand? A significant amount of work has gone in this direction.%, such as \cite{WeberCIG09,SynnaeveCIG11,SynnaeveAIIDE11,OntanonMSR10}.
\item {\em In-game learning}: How can bots deploy online learning techniques that allow them to improve their game play while playing a game? These techniques might include reinforcement learning techniques, but also opponent modeling. The main problem again is the fact that the state space is too large and the fact that RTS games are partially observable.
\item {\em Inter-game learning}: What can be learned from one game that can be used to increase the chances of victory in the next game? Some work has used simple game-theoretical solutions to select amongst a pool of predefined strategies, but the general problem remains unsolved.
\end{itemize}

@@

\subsubsection{Spatial and Temporal Reasoning}
% TODO just a paragraph on exposing why there are temporal and spatial
% reasoning in RTS AI.
Spatial  reasoning   is  related  to   each  aspect  of   terrain
exploitation.  Spatial reasoning is involved in tasks such as building placing, or base expansion. In the former, the player needs to
carefully  consider building  position  into its  own  bases to  both
protect them  by creating  a wall against  invasions and to  avoid bad
configurations  where large  units could  be stuck. In base expansion, the player has to
choose good available emplacements to  build a new base, regarding its
own  position  and opponent's  bases.  Finally,  spatial reasoning  is
key to tactical reasoning: players need to decide where to place units
for battle,  favoring, for  instance, engagements when  the opponent's
units are into a bottleneck.

@@

Analogously, temporal reasoning is key in tactical or strategic reasoning. For example, timing attacks and retreats to gain advantage. At a higher strategic level, players need to reason about when to perform long-term impact economic actions such as upgrades, building construction, strategy switching, etc. all taking into account that the effects of these actions are not immediate, but longer term.

\subsubsection{Domain Knowledge Exploitation}
In traditional board-games such as Chess, researchers have exploited the large amounts of existing domain knowledge to create good evaluation functions to be used by alpha-beta search algorithms, extensive opening books, or end-game tables. In the case of RTS games, it is still unclear the ways in which the significantly large amount of domain knowledge (in the forms or strategy guides, replays, etc.) can be exploited by bots. Most work in this area has focused on two main directions: on the one hand, researchers are finding ways in which to hard-code existing strategies into bots, so that bots only need to decide which strategies to deploy, instead of having to solve the complete problem of deciding which actions to execute by each individual unit at each time step. One the other hand, large datasets of replays have been created \cite{WeberCig09,synnaeve2012dataset}, from where strategies, trends or plans have been tried to learn. However, StarCraft games are quite complex, and how to automatically learn from such datasets is still an open problem.

\subsubsection{Task Decomposition}
For all the previous reasons, most existing approaches to play games like StarCraft work by decomposing the problem of playing a RTS game into a collection of smaller problems, to be solved independently. Specifically, a common subdivision is:
\begin{itemize}
\item {\em Strategy}: corresponds to the high-level decision making process.  This is
  the  highest level of  abstraction for  the game  comprehension. Finding   an   efficient   strategy   or
  counter-strategy  against a  given opponent is key in RTS games.  It concerns  the whole
  set of  units and buildings  a player owns. %If  we may allow  ourselves a  military analogy, strategy is orders given by generals at the HQ. 
\item  {\em Tactics}: are  the implementation  of the  current  strategy. It
  implies  army and  building positioning,  movements, timing,  and so
  on.  Tactics concerns a  group of  units. %They  are orders  given by officers on the battlefield.
\item  {\em Reactive  control}: is  the  implementation  of  tactics.  This
  consists   in  moving,   targeting,  firing,   fleeing,  hit-and-run
  techniques (a.k.a. ``kiting'')  during battle. Reactive control focuses
  on a specific unit. %It is soldiers applying officers' orders. 
%\end{itemize}
%
%\noindent
%Both     strategy      and     tactics     are      usually     called
%\textit{macro-management},  whereas reactive  control  is also  called
%\textit{micro-management}. In addition of the three tasks shown above,
%one could also consider these two tasks that an AI has to deal with:
%\begin{itemize}
\item {\em Terrain analysis}: consists  in the analysis of regions composing
  the  map:  choke-points,  minerals  and  gas emplacements,  low  and  high
  walkable grounds, islands, etc.
\item {\em Intelligence gathering}:  corresponds to information collected about
  the  opponent. Because of  the fog-of-war,  players must
  regularly send scouts to localize and spy enemy bases.%, and must see or  infer what buildings and technology the enemy has developed in order  to adapt its strategy.
\end{itemize}

In comparison, when humans play StarCraft, they typically divide their decision making in a very different way. The StarCraft community typically talk about two tasks:
\begin{itemize}
  \item {\em Micro}: is the ability to control your units individually. A good \emph{micro} player usually keeps their units alive during more time.
  \item {\em Macro}: is the ability to produce units and to expand at the appropriate times to keep your production of units flowing. A good \emph{macro} player usually has the larger army.
\end{itemize}

The reader can find a  good presentation of task decomposition for AIs
playing RTS in~\cite{weber2011acs}. Although the previous task decomposition is common, a significant challenge is on designing architectures so that the individual AI techniques that address each of those tasks can communicate and effectively work together, resolving conflicts, prioritizing resources between them, etc. Section \ref{sec:integration} provides an overview of the task decompositions that state-of-the-art bots use.
